---
title: "Social Pain by SES: By-Item Analysis"
author: "Qing Honors Thesis: Study 1"
date: "`r format(Sys.time(), '%H:%M, %d %B, %Y')`"
output:
  html_document:
    toc: yes
    toc_depth: 4
    toc_float: yes
    number_sections: no
  pdf_document:
    toc: yes
    toc_depth: '4'
editor_options:
  chunk_output_type: console
---

# Social Pain by SES (By-Item Analysis)

> **Are low-SES targets (those paired with low SES jobs) perceived as less sensitive to socially painful events than high-SES targets (those paired with high SES jobs)?**

**Methods**
Within-subjects design: 67 Mturkers rated how much pain 10 high and 10 low SES targets were expected to feel following socially painful events (e.g., losing a family pet). Only participants who passed 70% or more of the manipulation checks were included in the analysis - see cleaning script (1_social_pain_SES_clean.R) for full cleaning process. 

# R Session Set Up

The first *option* below, `error=TRUE`, keeps `knitr`/RMarkdown knitting even if it encounters an error in R code. The second *option*, `fig.asp=1`, sets the default aspect ratio of figures to 1.0. 

```{r}
knitr::opts_chunk$set(error=TRUE , fig.asp=1 )
```

Housekeeping: Clear memory and graphics. 

```{r}
rm(list=ls())  # Clears all the variables from memory. 
graphics.off() # Clears all the graphs.
```


-------------------------------------------------------------------------


# 1. Social Pain X SES

## 1.A. Load Packages  

```{r}
library(effectsize)
library(tidyverse)
```


## 1.B. Read in Data from WD 

We will fit a paired samples t-test, examining if participants had significantly different social pain ratings across SES. 

```{r}

# Read in csv 
setwd("C:/Users/freib/OneDrive - Indiana University/Research/Qing_HonorsThesis/SocialPainXSES_Markdown_10-6-2021/By-Item-Clean")
dat = read.csv("social_pain_SES_clean_data_by-item.csv")

```

# 2. By-Item Analysis 

## Models {.tabset .tabset-fade .tabset-pills}
### 2.A. Item 1
```{r}
#Item 1: This person's best friend moves across the country
d1 <- dat %>% 
  filter(item=="1") 
unique(d1$item)

# Define Model
t.test(mean_pain ~ SES, paired = TRUE, data = d1)

d1 %>%
  group_by(SES) %>%
  summarise(M = mean(mean_pain), SD = sd(mean_pain)) -> mean_d1

mean_d1

# Cohen's D 
cohens_d(mean_pain ~ SES, 
         data = d1, 
         paired = TRUE)

```

### 2.B. Item 2
```{r}
#Item 2: This person realizes after walking around all day that a pair of underwear was stuck to the back of their shirt.

d2 <- dat %>% 
  filter(item=="2") 
unique(d2$item)

# Define Model
t.test(mean_pain ~ SES, paired = TRUE, data = d2)

d2 %>%
  group_by(SES) %>%
  summarise(M = mean(mean_pain), SD = sd(mean_pain)) -> mean_d2

mean_d2

# Cohen's D 
cohens_d(mean_pain ~ SES, 
         data = d2, 
         paired = TRUE)

```

### 2.C. Item 3
```{r}
#Item 3: Strangers laugh at this person's haircut.

d3 <- dat %>% 
  filter(item=="3") 
unique(d3$item)

# Define Model
t.test(mean_pain ~ SES, paired = TRUE, data = d3)

d3 %>%
  group_by(SES) %>%
  summarise(M = mean(mean_pain), SD = sd(mean_pain)) -> mean_d3

mean_d3

# Cohen's D 
cohens_d(mean_pain ~ SES, 
         data = d3, 
         paired = TRUE)

```


### 2.D. Item 4
```{r}
#Item 4: This person's best friend gossips about them behind their back.

d4 <- dat %>% 
  filter(item=="4") 
unique(d4$item)

# Define Model
t.test(mean_pain ~ SES, paired = TRUE, data = d4)

d4 %>%
  group_by(SES) %>%
  summarise(M = mean(mean_pain), SD = sd(mean_pain)) -> mean_d4

mean_d4

# Cohen's D 
cohens_d(mean_pain ~ SES, 
         data = d4, 
         paired = TRUE)

```


### 2.E. Item 5
```{r}
#Item 5: A friend makes fun of this person in front of others.

d5 <- dat %>% 
  filter(item=="5") 
unique(d5$item)

# Define Model
t.test(mean_pain ~ SES, paired = TRUE, data = d5)

d5 %>%
  group_by(SES) %>%
  summarise(M = mean(mean_pain), SD = sd(mean_pain)) -> mean_d5

mean_d5

# Cohen's D 
cohens_d(mean_pain ~ SES, 
         data = d5, 
         paired = TRUE)

```


### 2.F. Item 6
```{r}
#Item 6: This person invites friends over to celebrate their birthday and no one comes.

d6 <- dat %>% 
  filter(item=="6") 
unique(d6$item)

# Define Model
t.test(mean_pain ~ SES, paired = TRUE, data = d6)

d6 %>%
  group_by(SES) %>%
  summarise(M = mean(mean_pain), SD = sd(mean_pain)) -> mean_d6

mean_d6

# Cohen's D 
cohens_d(mean_pain ~ SES, 
         data = d6, 
         paired = TRUE)

```


### 2.G. Item 7
```{r}
#Item 7: This person overhears a coworker talking about their incompetence at their job.

d7 <- dat %>% 
  filter(item=="7") 
unique(d7$item)

# Define Model
t.test(mean_pain ~ SES, paired = TRUE, data = d7)

d7 %>%
  group_by(SES) %>%
  summarise(M = mean(mean_pain), SD = sd(mean_pain)) -> mean_d7

mean_d7

# Cohen's D 
cohens_d(mean_pain ~ SES, 
         data = d7, 
         paired = TRUE)

```


### 2.H. Item 8
```{r}
#Item 8: This person's family pet passes away.

d8 <- dat %>% 
  filter(item=="8") 
unique(d8$item)

# Define Model
t.test(mean_pain ~ SES, paired = TRUE, data = d8)

d8 %>%
  group_by(SES) %>%
  summarise(M = mean(mean_pain), SD = sd(mean_pain)) -> mean_d8

mean_d8

# Cohen's D 
cohens_d(mean_pain ~ SES, 
         data = d8, 
         paired = TRUE)

```


### 2.I. Item 9.
```{r}
#Item 9: This person trips and falls and people laugh at them.

d9 <- dat %>% 
  filter(item=="9") 
unique(d9$item)

# Define Model
t.test(mean_pain ~ SES, paired = TRUE, data = d9)

d9 %>%
  group_by(SES) %>%
  summarise(M = mean(mean_pain), SD = sd(mean_pain)) -> mean_d9

mean_d9

# Cohen's D 
cohens_d(mean_pain ~ SES, 
         data = d9, 
         paired = TRUE)

```


### 2.J. Item 10
```{r}
#Item 10: This person's romantic partner asks them for some “space”.

d10 <- dat %>% 
  filter(item=="10") 
unique(d10$item)

# Define Model
t.test(mean_pain ~ SES, paired = TRUE, data = d10)

d10 %>%
  group_by(SES) %>%
  summarise(M = mean(mean_pain), SD = sd(mean_pain)) -> mean_d10

mean_d10

# Cohen's D 
cohens_d(mean_pain ~ SES, 
         data = d10, 
         paired = TRUE)

```



-------------------------------------------------------------------------

# R Session Info

To help with reproducibility, it is important to include the date and details of the software versions:

```{r}
date()
sessionInfo()
```

